Tidy data structure to support exploration and modeling of temporal data

### 2018-11-25 main.Rmd
rewrote sub-section on "interval"

Additional representations are provided, like year-month, year-quarter. Extensible. Custom index classes can be supported.

@@

For data indexed in regular time space, the time interval is obtained by computing the greatest common divisor based on the non-negative differences of a given time index, although the data may include implicit time gaps. This implies that all the units in the table must share a common interval. It is relatively easy to determine if the data is daily or sub-daily since most statistical packages have built-in time representations for date-times and dates, for example their corresponding classes `POSIXct` and `Date` in R. However these turn out inappropriate for weekly, monthly and quarterly data. For example, the smallest time unit of monthly data is months in a year, which is equispaced points in a year. However, using the first day of the month can range from 28 to 31 days, which is irregularly spaced. A genuine year-month representation should avoid associating days with its format. Displaying the year and month components suffice to signal its monthly aggregated values instead of observed values at a particular timestamp. This argument is also applicable to the creation of year-week and year-quarter. (coercion)

@@

Buja et al. (1988) [-@viewing-pipeline] describes a viewing pipeline for interactive statistical graphics, that takes control of the transformation from data to plot. @xgobi, @ggobi, @orca, @plumbing and @xie2014reactive implemented data pipelines for the interactive statistical software **xgobi**, **ggobi**, **orca**, **plumbr** and **cranvas**, respectively. The pipeline is typically described with a one way flow, from data to plot. For interactive graphics, where all plots need to be updated when a user interacts with one plot, the events typically trigger the data pipeline to be run. @xie2014reactive uses a reactive programming framework, to implement the pipeline, in which user's interactions trigger a sequence of modules to update their views, that is, practically the same as running the data pipeline producing each plot.

>>>>

How to handle time zone. Additional representations are provided, like year-month, year-quarter. Extensible. Custom index classes can be supported.

It is relatively easy to determine if the data is daily or sub-daily since most statistical packages have built-in time representations for date-times and dates, for example their corresponding classes `POSIXct` and `Date` in R. However these turn out inappropriate for weekly, monthly and quarterly data. For example, the smallest time unit of monthly data is months in a year, which is equispaced points in a year. However, using the first day of the month can range from 28 to 31 days, which is irregularly spaced. A genuine year-month representation should avoid associating days with its format. Displaying the year and month components suffice to signal its monthly aggregated values instead of observed values at a particular timestamp. This argument is also applicable to the creation of year-week and year-quarter. (coercion)

@@

One of the cornerstones beneath a tsibble is time interval. This information plays a critical role in computing statistics (e.g. seasonal unit root tests) and building models (e.g. seasonal ARIMA). The principal divide is regularly or irregularly spaced in time. Since a tsibble permits implicit missing time, it is impossible to distinguish regularity from the index. It relies on user's specification by switching the `regular` argument off, when the data involves irregular intervals. This type of data can flow into event-based data modelling, not models that expect time series.

As for data indexed in regular time space, the time interval is derived by first computing absolute differences of time indices and then the greatest common divisor, which covers all conceivable cases. This implies that all subjects in a tsibble have one and the only interval. Data collected at different intervals should be organized in separate tsibbles, encouraging well-tailored analysis and models, because each subject may underly different data generating process.

@@

@viewing-pipeline describes a viewing pipeline for interactive statistical graphics, that takes control of the transformation from data to plot. @xgobi, @ggobi, @orca, @plumbing and @xie2014reactive implemented data pipelines for the interactive statistical software **xgobi**, **ggobi**, **orca**, **plumbr** and **cranvas**, respectively. The pipeline is typically described with a one way flow, from data to plot. For interactive graphics, where all plots need to be updated when a user interacts with one plot, the events typically trigger the data pipeline to be run. @xie2014reactive uses a reactive programming framework, to implement the pipeline, in which user's interactions trigger a sequence of modules to update their views, that is, practically the same as running the data pipeline producing each plot.
